Followers Are Not Enough: A Multi-faceted Approach to Community Detection in Online Social Networks

### 2014-11-24 paper-postreview/results.tex
Attempting to fix latexdiff version.
Still needs work.

As a sanity check, it is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest PV-AC. Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee. Said differently, users with the highest PV-AC in an activity-based community provide the highest reduction in uncertainty about that communities activity or inactivity on Twitter. Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency. This means that these accounts have high predictive capacity in terms of their followers' activity on Twitter. This is not surprising as these activity-based communities heavily overlapped with the topic-based communities that discuss Colorado (mentioned above) and these accounts provide information on this topic. This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity for a communities activity on a social media network. However, more work needs to be done to quantify this more fully.

At the individual-based level, we also found some interesting examples of multifaceted community membership, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to.
For example, the user @JohnReaves belongs to two different topic communities: one about healthcare and the other about innovation and creativity. There is a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community. This means that the user interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
Another interesting example is given by user @jenajean. She also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado. The activity-based community they belong to highly overlaps with the topic community (therefore they behave alike the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap with the topic community but for two users maximum.

>>>>

As a sanity check, it is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest PV-AC. Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee. Said differently, users with the highest PV-AC in an activity-based community provide the highest reduction in uncertainty about that communities activity or inactivity on Twitter. Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find $@$Colorado, which is the state official Twitter account, $@$ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency. This means that these accounts have high predictive capacity in terms of their followers' activity on Twitter. This is not surprising as these activity-based communities heavily overlapped with the topic-based communities that discuss Colorado (mentioned above) and these accounts provide information on this topic. This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity for a communities activity on a social media network. However, more work needs to be done to quantify this more fully.

At the individual-based level, we also found some interesting examples of multifaceted community membership, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to.
For example, the user $@$JohnReaves belongs to two different topic communities: one about healthcare and the other about innovation and creativity. There is a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community. This means that the user interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
Another interesting example is given by user $@$jenajean. She also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
Lastly, $@$rajean, $@$Tekee, $@$Kimbirly and $@$mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado. The activity-based community they belong to highly overlaps with the topic community (therefore they behave alike the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap with the topic community but for two users maximum.
